\documentclass[10pt, a4paper]{article}
\usepackage{lrec2006}
\usepackage{graphicx}

\usepackage{url}

\usepackage[utf8]{inputenc}
\usepackage{multirow} 
\usepackage[small,bf]{caption} 

%% \usepackage{multibib}
%%\usepackage[comma]{natbib}
%% \usepackage{chapterbib}

\usepackage{lingmacros}
\usepackage{threeparttable}

\usepackage{fancyvrb} 
\DefineVerbatimEnvironment{outputExample}{Verbatim}{fontsize=\small}
\DefineVerbatimEnvironment{goldExample}{BVerbatim}{fontsize=\tiny}

\bibdata{apertium-hbs-slv}

\newcommand{\sentenceexample}[1]{{\small\enumsentence{#1}}}

\title{Shallow-transfer rule-based machine translation for the Western group of South Slavic languages}

\name{Hrvoje Peradin, Filip Petkovsky, Francis M. Tyers}
%\name{X, Y, Z}

%\address{A, B, C}
\address{University of Zagreb, University of Zagreb, Institut for språkvitskap \\
               Faculty of Science, Faculty of Electrical Engineering, Det humanistiske fakultet \\
               Dept. of Mathematics, and Computer Science, N-9037 Universitetet i Tromsø\\
               hperadin@gmail.com, filip.petkovski@fer.hr, ftyers@prompsit.com\\}


\abstract{
The South Slavic languages, spoken mostly in the Balkans, make up one
of the three Slavic branches. The South Slavic branch is in turn
comprised of two subgroups, the Eastern subgroup containing Macedonian
and Bulgarian, and the western subgroup containing Serbo-Croatian
and Slovenian. This paper describes the development of a
bidirectional machine translation system for the western branch of
South-Slavic languages — Serbo-Croatian and Slovenian. Both
languages have a free word order, are highly inflected, and share a
great degree of mutual inteligibility. They are also under-resourced
as regards free/open-source resources. We give details on the resources and
development methods used, as well as an evaluation, and
general directions for future work.
 \\ \newline %\Keywords{keyword A, keyword B, keyword C}
}

\begin{document}

\maketitleabstract

\input{introduction}

\input{design}

% Development; also contains disambiguation, lexical transfer, and structural transfer
\input{development}

\input{disambiguation}

\input{lexicaltransfer}

\input{transfer}

% Tables:

\begin{table}

\begin{center}
\begin{tabular}{|l|rrr|}
\hline
\textbf{Dictionary} & \textbf{Paradigms} & \textbf{Entries} & \textbf{Forms} \\
\hline
Serbo-Croatian &  1,033 & 13,206 & 233,878 \\
Slovenian &  1,909 & 13,383 & 147,580 \\
\hline
Bilingual &  69 &  16,434 & -- \\
\hline
\end{tabular}
\caption{Statistics on number of lexicon entries for each of the dictionaries in the 
   system.}
\label{table:lexicons}
\end{center}

\end{table}

\begin{table}
\begin{center}
\begin{tabular}{|l|rr|}
\hline
 \textbf{Type}      & \texttt{hbs}$\rightarrow$\texttt{slv} & \texttt{slv}$\rightarrow$\texttt{hbs}\\
\hline
Disambiguation      &     194              &     28 \\
Lexical selection   &     --            &  42 \\
Transfer            &                47 &  98 \\
\hline

\end{tabular}
 \caption{Statistics on the number of rules in each direction. For the lexical selection rules, 
   the number indicates that there are 42 rules for each of the three standard varieties currently
   supported.}
\label{table:rules}
\end{center}
\end{table}

% EVALUATION 
\input{evaluation}


% CONCLUSIONS AND FUTURE WORK
\input{conclusions}

\section*{Acknowledgements}

The development of this language pair was funded as a part of the
Google Summer of Code.\footnote{\url{http://code.google.com/soc/}}
Many thanks to the language pair co-author Ale\v{s} Horvat and his
mentor Jernej Vičič, and other Apertium contributors for their
invaluable help and support.


%\nocite{*}

\bibliographystyle{lrec2006}
\bibliography{apertium-hbs-slv}

\end{document}

