\section{Evaluation}
\input{coveragetable}
This sections covers the evaluation of the developed system. 
The system was tested by measuring the lexical coverage, and by performing
a qualitative and a quantitative evaluation. 

Lexical coverage was tested using existing free corpora, 
while the quantitative evaluation was performed on 100 postedited sentences (with 1,055 words in
total) from the Slovenian news portal 
Delo. \footnote{\url{http://www.delo.si/}}

Statistics on the size of the resulting lexicons are given in table
\ref{table:lexicons}, and the rule counts are listed in table
\ref{table:rules}. While the lexicons are evenly matched, the number
of rules is slightly in favour of the \texttt{hbs} side. This is due
to the fact that after the initial development phase additional work
has been done in the transfer module for the \texttt{slv}
$\rightarrow$ \texttt{hbs} direction, and the disambiguation and
lexical selection modules have been developed by native speakers of
Serbo-Croatian who are not fluent in Slovene.

\subsection{Lexical coverage}

Coverage for the Serbo-Croatian--Slovenian language pair was measured using both the SETimes \cite{tyers2010south} and Europarl \cite{koehn05a} corpora. 
We measured coverage naively, meaning that we assume a word is in our 
dictionaries if at least one of its surface forms is found in the corpus. 
We are aware of the shortcomings of such an evaluation framework, 
however we decided to use it because of its simplicity.

The Serbo-Croatian $\rightarrow$ Slovenian side was evaluated using the SETimes corpus.
As SETimes does not cover Slovenian
the Slovenian $\rightarrow$ Serbo-Croatian side was evaluated only on the EuroParl corpus. The results are shown in table \ref{table:coverage}.

\subsection{Quantitative}

The quantitative evaluation was performed by 5 articles
from the Slovenian news portal Delo.
The articles were translated from Slovenian using Apertium, and were later corrected by a human post-editor in order to get a correct translation.
The Word Error Rate (WER) was calculated
by counting the number of insertions, substitutions and deletions between the post-edited articles
and the original translation. We used the freely available \texttt{apertium-eval-translator} for calculating the WER 
and for bootstrap resampling \cite{koehn04}.
We also reported the percentage of out of vocabulary words (OOV), and the total number of words per article.
The results are given in table \ref{table:quantitative1}.

We also calculated both metrics for the output of Google Translate\footnote{\url{http://translate.google.com/}} 
and the results are presented in the same tables. Note that to compare the systems
we made two posteditions, one from the Apertium translation, and the other 
from the Google translation, so as not to bias the evaluation in either direction.

The post-editting evaluation shows comparable results for our system
and Google Translate according to WER and PER metrics.  The Slovenian
$\rightarrow$ Serbo-Croatian translation seems to be better than the
Serbo-Croatian $\rightarrow$ Slovenian one which is due to the fact
that more effort was put into developing the former direction.

\input{quantitativeevaluationtable}

\subsection{Qualitative}
The biggest problems are currently caused by the incompleteness of our dictionaries.
The issues caused by OOV words are twofold.
The less important issue is the fact that the system is unable to provide a translation for the unknown words ---
although in many cases, such as with proper names, these may result in \emph{free rides}, that is the word
is the same in both languages.
However, the more important issue is that OOV words cause problems with disambiguation and transfer, since they
break long chains of words into smaller ones and drastically reduce context information. 

Next, we have seen that the number of disambiguation rules for
Slovenian is not sufficient for high-quality disambiguation.  The
constraint grammar for the Slovenian side was written based on the
constraint grammar for the Serbo-Croatian side, and it needs further
work.\footnote{An evaluation of a more extensive Constraint
  grammar for Croatian can be found in \cite{peradin2012towards}}

We have also noticed difficulties in the transfer because of the loose
grammar of both sides. Variations created by the free word order, and
long distance relationships between sentence constituents make it
difficult to write translation rules that cover a wide variety of
language constructs. Adding additional rules does not significantly
improve the performance of the system and OOV words make long transfer
rules irrelevant.

Finally, because of the short timeframe, and due to the fact no
reliable parallel corpus exists for this language pair,\footnote{There
is e.g. \url{http://opus.lingfil.uu.se/}, but it consists mostly of
texts from OpenSubtitles} we were unable to do much work on lexical selection.
Our lexical-selection module is the least developed part of our
system. We have not done any work on the Slovenian side and the number
of rules for the Serbo-Croatian side is small.
