\subsection{Lexical transfer}
The lexical transfer was done with an \emph{lttoolbox} letter
transducer composed of bilingual dictionary entries.

In addition to standard word-by-word pairing of translations,
additional paradigms were added to the transducer to handle
less general tagset mismatches, that were deemed more convenient to
be resolved directly.
However, to minimize manual correction of tag mismatches, most of the
tagset differences were handled with macros in the structural transfer
module.

The bilingual dictionary was also used to introduce tags for
tricky cases such as when the adjective comparison is synthetic on one
side, and analytic on the other (e.g. \emph{zdravije} vs. \emph{bolj zdravo}).
This difference is arbitrary, and unfortunately every such occurence
needed to be marked by hand. These tags were expanded to the correct
form later in structural transfer.

\subsection{Lexical selection}

Since there was no adequate and free Slovenian -- Serbo-Croatian parallel corpus, 
we chose to do the lexical selection relying only on hand-written rules in 
Apertium's lexical selection module \cite{tyers12a}.
For cases not covered by our hand-written rules, the system would choose the 
default translation from the bilingual dictionary.
We provide examples of such lexical selection rules.

Phonetics-based lexical selection: many words from the Croatian and Serbian dialects differ in a single phoneme.
An example are the words \emph{točno} in Croatian and \emph{tačno} in Serbian (engl. \emph{accurate}).
Such differences were solved through the lexical selection module using rules like:

{\small
\begin{Verbatim}
<rule>
  <match lemma="točno" tags="adv.*">
    <select lemma="točno" tags="adv.*"/>
  </match>
</rule>
\end{Verbatim}
}
for Croatian, and
{\small
\begin{Verbatim}
<rule>
  <match lemma="točno" tags="adv.*">
    <select lemma="tačno" tags="adv.*"/>
  </match>
</rule>
\end{Verbatim}
}
for Serbian and Bosnian.

Similarly, the Croatian language has the form \emph{burza} (meaning stock exchange in English), while Serbian and Bosnian have \emph{berza}. 
For those forms the following rules were written:

{\small
\begin{Verbatim}
<rule>
  <match lemma="borza" tags="n.*">
    <select lemma="burza" tags="n.*"/>
  </match>
</rule>
\end{Verbatim}
}
for Croatian, and 
{\small
\begin{Verbatim}
<rule>
  <match lemma="borza" tags="n.*">
    <select lemma="berza" tags="n.*"/>
  </match>
</rule>

\end{Verbatim}
}

for Serbian and Bosnian.

Another example of a phonetical difference are words which have h in Croatian and Bosnian, but v in Serbian.
Such words include \emph{kuha} and \emph{duhan} in Croatian and Bosnian, but \emph{kuva} and \emph{duvan} in Serbian.
Similar rules were written for the forms for \emph{porcelain} (procelan in Serbian and porculan in Croatian), 
\emph{salt} (so and sol) and so on.

While the Serbian dialect accepts the Ekavian and Ikavian reflexes, 
the Croatian dialect uses only the Ijekavian reflex.
Since the selection for the different reflexes of the \emph{yat} vowel is done in the generation process,
no rules were needed in the lexical selection module.

Internationalisms have been introduced to Croatian and Bosnian mainly through the Italian and German languages
whereas they have entered Serbian through French and Russian. 
As a result, the three dialects have developed different phonetic patterns for international words.

Examples of rules for covering such varieties include:
{\small
\begin{Verbatim}
<rule>
  <match lemma="Betlehem" tags="np.*">
    <select lemma="Betlehem" tags="np.*"/>
  </match>
</rule>
\end{Verbatim}
}
for Croatian and Bosnian, and
{\small
\begin{Verbatim}
<rule>
  <match lemma="Betlehem" tags="np.*">
    <select lemma="Vitlejem" tags="np.*"/>
  </match>
</rule>
\end{Verbatim}
}
for Serbian.

Finally, the Croatian months used for the Gregorian calendar have Slavic-derived names and differ from the original Latin names.
For example, the Croatian language has the word \emph{siječanj} for \emph{January}, and 
the Serbian language has the word \emph{januar}.
These differences were also covered by the lexical selection module.

% This is not lexical ambiguity;
%% Besides the \emph{yat} reflex, several other cases were not covered in the lexical selection module. These 
%% include the pronoun `what' which has the form \emph{što} in Croatian and the forms \emph{što} 
%% and \emph{šta} in Serbian and Bosnian, depending on whether the context is interrogative or 
%% relative. This ambiguity was left out of the lexical-selection module and was dealt with during generation.
% how?
% Hrvoje: Should be covered in Constraint Grammar by selecting correct
% tags, but it's not. Should be correctly marked in the lexicon, but
% it's not :)
